---
title: "Revenue comparison on watersheds"
author: "Jarad Niemi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, message=FALSE}
library(dplyr)
library(tidyr)
library(lme4)
library(lsmeans)
library(multcomp)
```

```{r}
sessionInfo()
```

This analysis will look at the revenue by watershed which accounts for the 
amount of crop area that has been converted to prairie.
The assumed prairie cost per acre is 

```{r}
prairie_cost_per_acre = 95
```


## Simple analysis

This analysis will calculate the mean difference in revenue for both corn and
soybean comparing the all crop (control) to the prairie treatment.

```{r}
df <- STRIPSTyndall::revenue %>%
  left_join(STRIPSMeta::watersheds) %>%
  left_join(STRIPSMeta::crop_seed_info) %>%
  filter(year > 2007) %>% # for PNAS paper we are not including 2007 (establishment)
  mutate(crop_prop = 1-prairie_pct/100,
         revenue = crop_prop * revenue - prairie_cost_per_acre * (1-crop_prop), 
         any_prairie = ifelse(treatment == "0% prairie", 
                              "No", 
                              "Yes")) 

df %>%
  group_by(block, any_prairie, crop_species) %>%
  summarize(mean = mean(revenue)) %>%
  spread(any_prairie, mean) %>%
  mutate(Diff = Yes - No) %>%
  group_by(crop_species) %>%
  summarize(mean_difference = mean(Diff, na.rm=TRUE))
```

## Using contrasts

Corn analysis

```{r}
corn <- df %>% 
  filter(crop_species == "corn") %>%
  dplyr::select(revenue, treatment, block, size_ha, watershed, year)
  
m <- lmer(revenue ~ treatment + block + size_ha + (1|watershed) + (1|year), data=corn)

# summary(m)

m %>%
  lsmeans("treatment") %>%
  contrast("trt.vs.ctrl", ref=2:4)
```



Soybean analysis


```{r}
soybean <- df %>% 
  filter(crop_species == "soybean") %>%
  dplyr::select(revenue, treatment, block, size_ha, watershed, year)
  
m <- lmer(revenue ~ treatment + block + size_ha + (1|watershed) + (1|year), 
          data=soybean)

summary(m)

m %>%
  lsmeans("treatment") %>%
  contrast("trt.vs.ctrl", ref=2:4)
```

