---
title: "Revenue comparison in crop areas"
author: "Jarad Niemi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, message=FALSE}
library(dplyr)
library(tidyr)
library(lme4)
library(lsmeans)
library(multcomp)
```

```{r}
sessionInfo()
```


This vignette compares crop revenue in the crop area of each watershed, 
i.e. it does not account for the fact that part of the watershed is now 
prairie in the treatment watersheds.
Thus, the aim is to investigate the effect of prairie on the crop.

## Simple analysis

This analysis will calculate the mean difference in revenue for both corn and
soybean comparing the all crop (control) to the prairie treatment.

```{r}
STRIPSTyndall::revenue %>%
  left_join(STRIPSMeta::watersheds) %>%
  left_join(STRIPSMeta::crop_seed_info) %>%
  filter(year > 2007) %>% # for PNAS paper we are not including 2007 (establishment)
  mutate(any_prairie = ifelse(treatment == "0% prairie", 
                              "No", 
                              "Yes")) %>%
  group_by(block, any_prairie, crop_species) %>%
  summarize(mean = mean(revenue)) %>%
  spread(any_prairie, mean) %>%
  mutate(Diff = Yes - No) %>%
  group_by(crop_species) %>%
  summarize(mean_difference = mean(Diff, na.rm=TRUE))
```

## Using contrasts

Corn analysis

```{r}
df <- STRIPSTyndall::revenue %>%
  left_join(STRIPSMeta::watersheds) %>%
  left_join(STRIPSMeta::crop_seed_info)
  
corn <- df %>% 
  filter(crop_species == "corn") %>%
  dplyr::select(revenue, treatment, block, size_ha, watershed, year)
  
m <- lmer(revenue ~ treatment + block + size_ha + (1|watershed) + (1|year), 
          data=corn)

# summary(m)

m %>%
  lsmeans("treatment") %>%
  contrast("trt.vs.ctrl", ref=2:4)
```



Soybean analysis


```{r}
soybean <- df %>% 
  filter(crop_species == "soybean") %>%
  dplyr::select(revenue, treatment, block, size_ha, watershed, year)
  
m <- lmer(revenue ~ treatment + block + size_ha + (1|watershed) + (1|year), 
          data=soybean)

summary(m)

m %>%
  lsmeans("treatment") %>%
  contrast("trt.vs.ctrl", ref=2:4)
```
